---
title: "heptathlon"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("/Users/aldosolari/Documents/mygithub/AE/data/heptathlon")
```

```{r, message=FALSE}
library(HSAUR2)
data("heptathlon")
head(heptathlon)
```

Results of the olympic heptathlon competition, Seoul, 1988.

A data frame with 25 observations on the following 8 variables.

hurdles
results 100m hurdles.

highjump
results high jump.

shot
results shot.

run200m
results 200m race.

longjump
results long jump.

javelin
results javelin.

run800m
results 800m race.

score
total score.

Details

The first combined Olympic event for women was the pentathlon, first held in Germany in 1928. Initially this consisted of the shot putt, long jump, 100m, high jump and javelin events held over two days. The pentathlon was first introduced into the Olympic Games in 1964, when it consisted of the 80m hurdles, shot, high jump, long jump and 200m. In 1977 the 200m was replaced by the 800m and from 1981 the IAAF brought in the seven-event heptathlon in place of the pentathlon, with day one containing the events-100m hurdles, shot, high jump, 200m and day two, the long jump, javelin and 800m. A scoring system is used to assign points to the results from each event and the winner is the woman who accumulates the most points over the two days. The event made its first Olympic appearance in 1984.

In the 1988 Olympics held in Seoul, the heptathlon was won by one of the stars of women's athletics in the USA, Jackie Joyner-Kersee. The results for all 25 competitors are given here.

Source

D. J. Hand, F. Daly, A. D. Lunn, K. J. McConway and E. Ostrowski (1994). A Handbook of Small Datasets, Chapman and Hall/CRC, London.